Visual Diagnostics of a Model Explainer

### 2019-03-15 papers/Visual Diagnostics of a Model Explainer/Visual Diagnostics of a Model Explainer Created by LIME.Rmd
updated stats paper to new name and outline added

---
title: "An Assessment of LIME Explanations from a Random Forest Models"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
                      fig.pos = "center")
```

@@

>>>>

---
title: "Visual Diagnostics of a Model Explainer"
subtitle: "Tools for the Assessment of LIME Explanations"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE)
```

Intended journal: ASA Data Science Journal

@@

- main objective of a model explainer: 
    - understand and explain model performance
- LIME does...
    - conceptually: models at two levels
        1. Simple = explainer model
        2. Complex = original "black box model"
    - usually: model predictions, maybe with ground truth
        - type I error
        - type II error
        - model is wrong in both cases
    - explanation is also a prediction
        - how reliable is that explanation?
          - we will present some tools that could help answer that question
          - we will show an example using this tools (bullet data)
          - we will mention some possible insights about LIME that these tools have shown us
            - explainer model generally has very low $R^2$ (probably due to binning)
            - "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
- Describe LIME including details on binning and linear regression in binned features and motivation for the binning
